Master thesis

### 2017-07-18 05-Results.Rmd
Sylviculture results

Most of functional traits had a significant long term influence on ecosystem outputs (figure \@ref(fig:ftVar)). Only specific maximum diameter **dmax** add higher diversity for greater orders implying better evenness in species distributions. Regarding functional composition, traits fixed to mean did not change other functional traits density distribution. Moreover, seedrain did not seem to affect aboveground biomass and final ecosystem height and diameter structure. Seedrain constant fixed to 2 or 20 seed per hectare seemed to have a similar effect. Lower seedrain implied faster decrease of stem above 10 cm dbh and higher number of stem above 30 cm diameter at breast height after ecosystem resilience to disturbance (approximately 50 years). Lower seedrain than default decreased basal area over time. In addition, lower seedrain than default decreased equitability by increasing abundance of abundant species and decreasing abundance of less abundant species. See [Appendix 4: Sensitivity analysis] for further details.

@@

```{r datatrans, echo=FALSE, fig.cap='Ecosystem outputs data transformation. Ecosystem outputs (**A**) are normalized by the control value over time to calculate resilience (**B**); resilience of different ecosystem outputs is then used in a multidimensional space to caluclate ecosystem distance to equilibrium (**C**); finally distance ot equilibirum is integrated over time in a cummulative sum (**D**). ', cache=TRUE, fig.height=8, fig.width=12, message=FALSE}
library(dplyr)
g_agb <- ecosystem %>% 
  left_join(., doe, by = 'sim') %>%
  filter(richness == 125) %>% 
  filter(cvh == 1) %>% 
  ggplot(aes(x = time, y = agb/1000, color = disturbance)) +
  geom_point() +
  xlab('Time (years)') +
  ylab('Aboveground biomass (tonC/ha)') +
  scale_color_discrete('Disturbance\nintensity\n(% of BA)')
g_resilience <- resilience %>% 
  left_join(., doe, by = 'sim') %>%
  filter(richness == 125) %>% 
  filter(cvh == 1) %>% 
  ggplot(aes(x = time, y = agb, color = disturbance)) +
  geom_hline(yintercept = 1, col = 'red') +
  geom_point() +
  xlab('Time (years)') +
  ylab('Resilience of aboveground biomass') +
  scale_color_discrete('Disturbance\nintensity\n(% of BA)')
g_deq <- deq %>% 
  left_join(., doe, by = 'sim') %>%
  filter(richness == 125) %>% 
  filter(cvh == 1) %>% 
  ggplot(aes(x = time, y = structure, color = disturbance)) +
  geom_hline(yintercept = 0, col = 'red') +
  geom_point() +
  xlab('Time (years)') +
  ylab('Distance to forest dynamic equilibrium\n(AGB, BA, N, N10 and N30)') +
  scale_color_discrete('Disturbance\nintensity\n(% of BA)')
g_Ieq <- Ieq %>% 
  left_join(., doe, by = 'sim') %>%
  filter(richness == 125) %>% 
  filter(cvh == 1) %>% 
  ggplot(aes(x = time, y = Ieq.structure, color = disturbance)) +
  geom_point() +
  xlab('Time (years)') +
  ylab('Cummulative integral of\ndistance to forest dynamic equilibrium\n(AGB, BA, N, N10 and N30)') +
  scale_color_discrete('Disturbance\nintensity\n(% of BA)')
cowplot::plot_grid(g_agb, g_resilience, g_deq, g_Ieq, labels = LETTERS[1:4])
```

The ranking was stable over time for the 240 simulations. So we used the cummulative integral after 600 years $Ieq_{600}$ as a measurement of ecosystem resilience. We compared cummulative integral after 600 years to communities taxonomic and functional diversity for each leavel of disturbance (see Figure \@ref(fig:gIeq)). We found that increased functional diversity [FDiv, @villeger_new_2008] was reducing cummulative integral from ecosystem distance to forest dynamic equilibrium after 600 years ($Ieq_{600}$). In addition, functional evenness was complementary reducing $Ieq_{600}$. Finally species richness was not directly link to $Ieq_{600}$. Effectivelly, low species richness could result in variant $Ieq_{600}$, but increased species richness resulted in increased functional diversity and consequently lower $Ieq_{600}$. We found similar results for all disturbance levels and other ecosystem functions (forest production and forest diversity, see [Appendix 5: Disturbance simulations]).

```{r gIeq, echo=FALSE, fig.cap='Ecosystem resilience after 600 years with taxonomic and functional diversity for different levels of disturbance. Cummulative integral from ecosystem distance to forest dynamic equilibrium after 600 years was represented against functional diversity [FDiv, @villeger_new_2008] for different level of disturbance (25, 50 and 75% of total basal area); dot shapes represents the species richness whereas dot color represents functional evenness [FEve, @villeger_new_2008].', cache=TRUE, fig.width=12}
Ieq %>% 
  left_join(., doe, by = 'sim') %>% 
  filter(time == 600) %>% 
  ggplot(aes(x = FDiv, y = Ieq.structure, label = sim)) + 
  geom_smooth(method = 'lm', alpha = 0.3, colour= 'grey') +
  geom_point(aes(shape = richness, color = FEve)) +
  facet_wrap(~disturbance, scales = "free", labeller = 'label_both') + 
  xlab('Functional diversity (FDiv)') +
  ylab('Cummulative integral from ecosystem 
       distance to forest dynamic equilibrium after 600 years') +
  scale_shape_discrete('Species\nrichness\n(SR)') +
  scale_color_continuous('Functional\nevenness\n(FEve)')
```

@@

>>>>

Most of functional traits had a significant long term influence on ecosystem outputs (figure \@ref(fig:ftVar)). Only specific maximum diameter dmax add higher diversity for greater orders implying better evenness in species distributions. Regarding functional composition, traits fixed to mean did not change other functional traits density distribution. Moreover, seedrain did not seem to affect aboveground biomass and final ecosystem height and diameter structure. Seedrain constant fixed to 2 or 20 seed per hectare seemed to have a similar effect. Lower seedrain implied faster decrease of stem above 10 cm dbh and higher number of stem above 30 cm diameter at breast height after ecosystem resilience to disturbance (approximately 50 years). Lower seedrain than default decreased basal area over time. In addition, lower seedrain than default decreased equitability by increasing abundance of abundant species and decreasing abundance of less abundant species. See [Appendix 4: Sensitivity analysis] for further details.

@@

```{r datatrans, echo=FALSE, fig.cap='Ecosystem outputs data transformation. Ecosystem outputs (**A**) are normalized by the control value over time to calculate resilience (**B**); resilience of different ecosystem outputs is then used in a multidimensional space to caluclate ecosystem distance to equilibrium (**C**); finally distance ot equilibirum is integrated over time in a cummulative sum (**D**). ', cache=TRUE, fig.height=8, fig.width=12, message=FALSE}
library(dplyr)
g_agb <- ecosystem %>% 
  left_join(., doe, by = 'sim') %>%
  filter(richness == 125) %>% 
  filter(cvh == 1) %>% 
  ggplot(aes(x = time, y = agb/1000, color = disturbance)) +
  geom_point() +
  xlab('Time (years)') +
  ylab('Aboveground biomass (tonC/ha)') +
  scale_color_discrete('Disturbance\nintensity\n(% of BA)')
g_resilience <- resilience %>% 
  left_join(., doe, by = 'sim') %>%
  filter(richness == 125) %>% 
  filter(cvh == 1) %>% 
  ggplot(aes(x = time, y = agb, color = disturbance)) +
  geom_hline(yintercept = 1, col = 'red') +
  geom_point() +
  xlab('Time (years)') +
  ylab('Resilience of aboveground biomass') +
  scale_color_discrete('Disturbance\nintensity\n(% of BA)')
g_deq <- deq %>% 
  left_join(., doe, by = 'sim') %>%
  filter(richness == 125) %>% 
  filter(cvh == 1) %>% 
  ggplot(aes(x = time, y = structure, color = disturbance)) +
  geom_hline(yintercept = 0, col = 'red') +
  geom_point() +
  xlab('Time (years)') +
  ylab('Distance to forest structure equilibrium\n(AGB, BA, N, N10 and N30)') +
  scale_color_discrete('Disturbance\nintensity\n(% of BA)')
g_Ieq <- Ieq %>% 
  left_join(., doe, by = 'sim') %>%
  filter(richness == 125) %>% 
  filter(cvh == 1) %>% 
  ggplot(aes(x = time, y = Ieq.structure, color = disturbance)) +
  geom_point() +
  xlab('Time (years)') +
  ylab('Cummulative integral of\ndistance to forest structure equilibrium\n(AGB, BA, N, N10 and N30)') +
  scale_color_discrete('Disturbance\nintensity\n(% of BA)')
cowplot::plot_grid(g_agb, g_resilience, g_deq, g_Ieq, labels = LETTERS[1:4])
```

The ranking was stable over time for the 240 simulations. So we used the cummulative integral after 600 years $Ieq_{600}$ as a measurement of ecosystem resilience. We compared cummulative integral after 600 years to communities taxonomic and functional diversity for each leavel of disturbance (see Figure \@ref(fig:gIeq)). We found that increased functional diversity [FDiv, @villeger_new_2008] was reducing cummulative integral from ecosystem distance to forest structure equilibrium after 600 years ($Ieq_{600}$). In addition, functional evenness was complementary reducing $Ieq_{600}$. Finally species richness was not directly link to $Ieq_{600}$. Effectivelly, low species richness could result in variant $Ieq_{600}$, but increased species richness resulted in increased functional diversity and consequently lower $Ieq_{600}$. We found similar results for all disturbance levels and forest functionning (see [Appendix 5: Disturbance simulations]).

```{r gIeq, echo=FALSE, fig.cap='Ecosystem resilience after 600 years with taxonomic and functional diversity for different levels of disturbance. Cummulative integral from ecosystem distance to forest structure equilibrium after 600 years was represented against functional diversity [FDiv, @villeger_new_2008] for different level of disturbance (25, 50 and 75% of total basal area); dot shapes represents the species richness whereas dot color represents functional evenness [FEve, @villeger_new_2008].', cache=TRUE, fig.width=12}
Ieq %>% 
  left_join(., doe, by = 'sim') %>% 
  filter(time == 600) %>% 
  ggplot(aes(x = FDiv, y = Ieq.structure, label = sim)) + 
  geom_smooth(method = 'lm', alpha = 0.3, colour= 'grey') +
  geom_point(aes(shape = richness, color = FEve)) +
  facet_wrap(~disturbance, scales = "free", labeller = 'label_both') + 
  xlab('Functional diversity (FDiv)') +
  ylab('Cummulative integral from ecosystem 
       distance to forest structure equilibrium after 600 years') +
  scale_shape_discrete('Species\nrichness\n(SR)') +
  scale_color_continuous('Functional\nevenness\n(FEve)')
```

@@

## Sylviculture

```{r sylviculture, echo=FALSE, message=FALSE}
library(dplyr)
library(reshape2)
library(ggplot2)
path <- '~/Documents/ECOFOG/Results/disturbance/sylviculture/data/'
load(file.path(path, 'DOE.Rdata'))
load(file.path(path, 'resilience.Rdata'))
load(file.path(path, 'BErecovery.Rdata'))
deq <- data.frame(
  time = resilience$time,
  sim = resilience$sim,
  structure = apply(resilience[c('agb', 'ba', 'n', 'n10', 'n30')], 1, 
                  function(x) sqrt(sum((rep(1, length(x)) - x)^2))),
  production = apply(resilience[c('gpp', 'npp', 'Rday', 'Rnight')], 1, 
                  function(x) sqrt(sum((rep(1, length(x)) - x)^2)))
)
sim <- unique(resilience$sim)
Ieq <- sapply(sim, function(s){
  data_s <- subset(deq, sim ==s)
  return(cbind(data_s[c(1,2)], cumsum(data_s[-c(1,2)])))
}, simplify = F) ; rm(sim)
Ieq <- data.frame(do.call('rbind', Ieq))
names(Ieq)[3:4] <- paste0('Ieq.', names(Ieq)[3:4])
```

We repeated design of experiments and simulations used for the disturbance simulations with the sylviculture module. But only 37 simulations included harvestable species. Moreover most of simulations included low harvestable volume resulting in a small disturbance from 0.5 to 2.0 $m^2.ha^{-1}$ (see Figure \@ref(fig:gIeqSylv)). Consequently most of disturbed volume was due to primary and secondary tracks and was not related to logged trees. Thus sylviculture module resulted in aggregated localized gaps but not in species selective disturbance. We found that, contrarily to previous results, functional richness was significantly ($p<0.01$) decreasing forest resilience see Figure \@ref(fig:gIeqSylv)). But the range of variation from resilience was really low ($2 < I_{eq_{600}} < 10$). And resilience was mainly due to the density of *Bocoa prouacensis* in the simulated mature forests. Effectively *Bocoa prouacensis* was often the main harvested species and possessed additionnally a quick recovery inside the model due to unrealisticaly advantageous parameters. Still we found that functional dispersion was decreasing resilience but not significantly (see [Appendix 6: Sylviculture simulations]). Finally, biodiversity net effect is almost undisturbed due to the low disturbance intensity from the sylviculture module and results did not show complementarity or selection effect in forest resilience (see [Appendix 6: Sylviculture simulations]).

```{r gIeqSylv, echo=FALSE, warning=FALSE, fig.cap='Ecosystem resilience after 600 years with taxonomic and functional diversity. Cummulative integral from ecosystem distance to forest structure equilibrium after 600 years normalized by disturbed basal area was represented against functional richness [FRic, @villeger_new_2008]. Dot color represents the species richness (nb) whereas dot size represents the disturbed basal area (m2/ha). Grey line represents the linear regression and grey area the confidence interval.', cache=TRUE}
Ieq %>% 
  left_join(., doe, by = 'sim') %>% 
  filter(time == 600) %>% 
  ggplot(aes(x = FRic, y = Ieq.structure/ba, label = sim)) + 
  geom_smooth(method = 'lm', alpha = 0.3, colour= 'grey') +
  geom_point(aes(color = richness, size = ba/16)) +
  xlab('Functional richness (FRic)') +
  ylab('Cummulative integral from ecosystem 
       distance to forest dynamic equilibrium after 600 years') +
  scale_color_discrete('Species\nrichness\n(SR)') +
  scale_size_continuous('Basla\narea\ndisturbed\n(m2/ha)')
```

### 2017-07-18 06-Discussion.Rmd
Sylviculture results

>>>>

Finally, sylviculture module implemented inside TROLL showed lacks of ability to reproduce selective logging with current design of experiments. Results did not seem to be usable and will not be discussed. The main issues was the ability of the model to simulate mature forest with correct abundancy of mature trees from commonly harvested species. Two solutions might be possible in the tunning of the model. First, forest inventories could be used to initialize the model instead of a bare soil resulting in realistic species abundances, especially for harvested species. Secondly, selective logging could focus on guilds of species meeting peculiar values of functional traits [as wood density, see @Huth2004; @Khler2004; @Ruger2008] allowing the model to harvest more volume in order to meet reality.

### 2017-07-18 11-Appendix5.Rmd
Thesis v1
Sylviculture results

Appendix 4 presents ecosystem resilience after 600 years with taxonomic and functional diversity for different levels of disturbance. It encompass all functionnal diversity components [FRIC, FEve, FDiv, and FDis, @villeger_new_2008]. And it presents results for both forest dynamic (Figure \@ref(fig:A5IeqStructureAll)) and forest production (Figure \@ref(fig:A5IeqProductionAll)).

```{r A5IeqStructureAll, echo=FALSE, fig.cap='Ecosystem resilience after 600 years with taxonomic and functional diversity for different levels of disturbance. Cummulative integral from ecosystem distance to forest dynamic equilibrium after 600 years was represented against functional diversity [FRIC, FEve, FDiv, and FDis, @villeger_new_2008] for different level of disturbance (25, 50 and 75% of total basal area); dot shapes represents the species richness.', cache=TRUE, fig.height=8, fig.width=12, message=FALSE}
library(dplyr)
library(reshape2)
Ieq %>% 
  left_join(., doe, by = 'sim') %>% 
  filter(time == 600) %>%
  select(Ieq.structure, disturbance, richness, FRic, FEve, FDiv, FDis) %>% 
  melt(id.vars = c('Ieq.structure', 'disturbance', 'richness')) %>% 
  ggplot(aes(x = Ieq.structure, y = value)) + 
  geom_smooth(method = 'lm', alpha = 0.3, colour= 'grey') +
  geom_point(aes(shape = richness)) +
  facet_grid(variable~disturbance, scales = "free", labeller = 'label_both') + 
  ylab('Functional diversity') +
  xlab('Cummulative integral from ecosystem 
       distance to forest dynamic equilibrium after 600 years') +
  scale_shape_discrete('Species\nrichness\n(SR)')
```

```{r A5IeqProductionAll, echo=FALSE, fig.cap='Ecosystem resilience after 600 years with taxonomic and functional diversity for different levels of disturbance. Cummulative integral from ecosystem distance to forest production equilibrium after 600 years was represented against functional diversity [FRIC, FEve, FDiv, and FDis, @villeger_new_2008] for different level of disturbance (25, 50 and 75% of total basal area); dot shapes represents the species richness.', cache=TRUE, fig.height=8, fig.width=12}
Ieq %>% 
  left_join(., doe, by = 'sim') %>% 
  filter(time == 600) %>%
  select(Ieq.production, disturbance, richness, FRic, FEve, FDiv, FDis) %>% 
  melt(id.vars = c('Ieq.production', 'disturbance', 'richness')) %>% 
  ggplot(aes(x = Ieq.production, y = value)) + 
  geom_smooth(method = 'lm', alpha = 0.3, colour= 'grey') +
  geom_point(aes(shape = richness)) +
  facet_grid(variable~disturbance, scales = "free", labeller = 'label_both') + 
  ylab('Functional diversity') +
  xlab('Cummulative integral from ecosystem 
       distance to forest production equilibrium after 600 years') +
  scale_shape_discrete('Species\nrichness\n(SR)')
```

>>>>

This appendix presents ecosystem resilience after 600 years with taxonomic and functional diversity for different levels of disturbance. It encompass all functionnal diversity components [FRIC, FEve, FDiv, and FDis, @villeger_new_2008]. And it presents results for both forest structure (Figure \@ref(fig:A5IeqStructureAll)) and forest functionning (Figure \@ref(fig:A5IeqProductionAll)).

```{r A5IeqStructureAll, echo=FALSE, fig.cap='Ecosystem resilience after 600 years with taxonomic and functional diversity for different levels of disturbance. Cummulative integral from ecosystem distance to forest structure equilibrium after 600 years was represented against functional diversity [FRIC, FEve, FDiv, and FDis, @villeger_new_2008] for different level of disturbance (25, 50 and 75% of total basal area); dot shapes represents the species richness.', cache=TRUE, fig.height=8, fig.width=12, message=FALSE}
library(dplyr)
library(reshape2)
Ieq %>% 
  left_join(., doe, by = 'sim') %>% 
  filter(time == 600) %>%
  select(Ieq.structure, disturbance, richness, FRic, FEve, FDiv, FDis) %>% 
  melt(id.vars = c('Ieq.structure', 'disturbance', 'richness')) %>% 
  ggplot(aes(x = Ieq.structure, y = value)) + 
  geom_smooth(method = 'lm', alpha = 0.3, colour= 'grey') +
  geom_point(aes(shape = richness)) +
  facet_grid(variable~disturbance, scales = "free", labeller = 'label_both') + 
  ylab('Functional diversity') +
  xlab('Cummulative integral from ecosystem 
       distance to forest structure equilibrium after 600 years') +
  scale_shape_discrete('Species\nrichness\n(SR)')
```

```{r A5IeqProductionAll, echo=FALSE, fig.cap='Ecosystem resilience after 600 years with taxonomic and functional diversity for different levels of disturbance. Cummulative integral from ecosystem distance to forest functionning equilibrium after 600 years was represented against functional diversity [FRIC, FEve, FDiv, and FDis, @villeger_new_2008] for different level of disturbance (25, 50 and 75% of total basal area); dot shapes represents the species richness.', cache=TRUE, fig.height=8, fig.width=12}
Ieq %>% 
  left_join(., doe, by = 'sim') %>% 
  filter(time == 600) %>%
  select(Ieq.production, disturbance, richness, FRic, FEve, FDiv, FDis) %>% 
  melt(id.vars = c('Ieq.production', 'disturbance', 'richness')) %>% 
  ggplot(aes(x = Ieq.production, y = value)) + 
  geom_smooth(method = 'lm', alpha = 0.3, colour= 'grey') +
  geom_point(aes(shape = richness)) +
  facet_grid(variable~disturbance, scales = "free", labeller = 'label_both') + 
  ylab('Functional diversity') +
  xlab('Cummulative integral from ecosystem 
       distance to forest functionning equilibrium after 600 years') +
  scale_shape_discrete('Species\nrichness\n(SR)')
```

### 2017-07-18 docs/master-thesis.tex
Sylviculture results

Most of functional traits had a significant long term influence on
ecosystem outputs (figure \ref{fig:ftVar}). Only specific maximum
diameter \textbf{dmax} add higher diversity for greater orders implying
better evenness in species distributions. Regarding functional
composition, traits fixed to mean did not change other functional traits
density distribution. Moreover, seedrain did not seem to affect
aboveground biomass and final ecosystem height and diameter structure.
Seedrain constant fixed to 2 or 20 seed per hectare seemed to have a
similar effect. Lower seedrain implied faster decrease of stem above 10
cm dbh and higher number of stem above 30 cm diameter at breast height
after ecosystem resilience to disturbance (approximately 50 years).
Lower seedrain than default decreased basal area over time. In addition,
lower seedrain than default decreased equitability by increasing
abundance of abundant species and decreasing abundance of less abundant
species. See
\protect\hyperlink{appendix-4-sensitivity-analysis}{Appendix 4:
Sensitivity analysis} for further details.

@@

The ranking was stable over time for the 240 simulations. So we used the
cummulative integral after 600 years \(Ieq_{600}\) as a measurement of
ecosystem resilience. We compared cummulative integral after 600 years
to communities taxonomic and functional diversity for each leavel of
disturbance (see Figure \ref{fig:gIeq}). We found that increased
functional diversity \citep[FDiv,][]{villeger_new_2008} was reducing
cummulative integral from ecosystem distance to forest dynamic
equilibrium after 600 years (\(Ieq_{600}\)). In addition, functional
evenness was complementary reducing \(Ieq_{600}\). Finally species
richness was not directly link to \(Ieq_{600}\). Effectivelly, low
species richness could result in variant \(Ieq_{600}\), but increased
species richness resulted in increased functional diversity and
consequently lower \(Ieq_{600}\). We found similar results for all
disturbance levels and other ecosystem functions (forest production and
forest diversity, see
\protect\hyperlink{appendix-5-disturbance-simulations}{Appendix 5:
Disturbance simulations}).

\begin{figure}[htbp]
\centering
\includegraphics{master-thesis_files/figure-latex/gIeq-1.pdf}
\caption{\label{fig:gIeq}Ecosystem resilience after 600 years with taxonomic
and functional diversity for different levels of disturbance.
Cummulative integral from ecosystem distance to forest dynamic
equilibrium after 600 years was represented against functional diversity
\citep[FDiv,][]{villeger_new_2008} for different level of disturbance
(25, 50 and 75\% of total basal area); dot shapes represents the species
richness whereas dot color represents functional evenness
\citep[FEve,][]{villeger_new_2008}.}
\end{figure}

@@

@@

@@

This appendix presents ecosystem resilience after 600 years with
taxonomic and functional diversity for different levels of disturbance.
It encompass all functionnal diversity components \citep[FRIC, FEve,
FDiv, and FDis,][]{villeger_new_2008}. And it presents results for both
forest dynamic (Figure \ref{fig:A5IeqStructureAll}) and forest
production (Figure \ref{fig:A5IeqProductionAll}).

\begin{figure}[htbp]
\centering
\includegraphics{master-thesis_files/figure-latex/A5IeqStructureAll-1.pdf}
\caption{\label{fig:A5IeqStructureAll}Ecosystem resilience after 600 years
with taxonomic and functional diversity for different levels of
disturbance. Cummulative integral from ecosystem distance to forest
dynamic equilibrium after 600 years was represented against functional
diversity \citep[FRIC, FEve, FDiv, and FDis,][]{villeger_new_2008} for
different level of disturbance (25, 50 and 75\% of total basal area);
dot shapes represents the species richness.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{master-thesis_files/figure-latex/A5IeqProductionAll-1.pdf}
\caption{\label{fig:A5IeqProductionAll}Ecosystem resilience after 600 years
with taxonomic and functional diversity for different levels of
disturbance. Cummulative integral from ecosystem distance to forest
production equilibrium after 600 years was represented against
functional diversity \citep[FRIC, FEve, FDiv, and
FDis,][]{villeger_new_2008} for different level of disturbance (25, 50
and 75\% of total basal area); dot shapes represents the species
richness.}
\end{figure}

@@

>>>>

Most of functional traits had a significant long term influence on
ecosystem outputs (figure \ref{fig:ftVar}). Only specific maximum
diameter dmax add higher diversity for greater orders implying better
evenness in species distributions. Regarding functional composition,
traits fixed to mean did not change other functional traits density
distribution. Moreover, seedrain did not seem to affect aboveground
biomass and final ecosystem height and diameter structure. Seedrain
constant fixed to 2 or 20 seed per hectare seemed to have a similar
effect. Lower seedrain implied faster decrease of stem above 10 cm dbh
and higher number of stem above 30 cm diameter at breast height after
ecosystem resilience to disturbance (approximately 50 years). Lower
seedrain than default decreased basal area over time. In addition, lower
seedrain than default decreased equitability by increasing abundance of
abundant species and decreasing abundance of less abundant species. See
\protect\hyperlink{appendix-4-sensitivity-analysis}{Appendix 4:
Sensitivity analysis} for further details.

@@

The ranking was stable over time for the 240 simulations. So we used the
cummulative integral after 600 years \(Ieq_{600}\) as a measurement of
ecosystem resilience. We compared cummulative integral after 600 years
to communities taxonomic and functional diversity for each leavel of
disturbance (see Figure \ref{fig:gIeq}). We found that increased
functional diversity \citep[FDiv,][]{villeger_new_2008} was reducing
cummulative integral from ecosystem distance to forest structure
equilibrium after 600 years (\(Ieq_{600}\)). In addition, functional
evenness was complementary reducing \(Ieq_{600}\). Finally species
richness was not directly link to \(Ieq_{600}\). Effectivelly, low
species richness could result in variant \(Ieq_{600}\), but increased
species richness resulted in increased functional diversity and
consequently lower \(Ieq_{600}\). We found similar results for all
disturbance levels and forest functionning (see
\protect\hyperlink{appendix-5-disturbance-simulations}{Appendix 5:
Disturbance simulations}).

\begin{figure}[htbp]
\centering
\includegraphics{master-thesis_files/figure-latex/gIeq-1.pdf}
\caption{\label{fig:gIeq}Ecosystem resilience after 600 years with taxonomic
and functional diversity for different levels of disturbance.
Cummulative integral from ecosystem distance to forest structure
equilibrium after 600 years was represented against functional diversity
\citep[FDiv,][]{villeger_new_2008} for different level of disturbance
(25, 50 and 75\% of total basal area); dot shapes represents the species
richness whereas dot color represents functional evenness
\citep[FEve,][]{villeger_new_2008}.}
\end{figure}

@@

\subsection{Sylviculture}\label{sylviculture-1}

We repeated design of experiments and simulations used for the
disturbance simulations with the sylviculture module. But only 37
simulations included harvestable species. Moreover most of simulations
included low harvestable volume resulting in a small disturbance from
0.5 to 2.0 \(m^2.ha^{-1}\) (see Figure \ref{fig:gIeqSylv}). Consequently
most of disturbed volume was due to primary and secondary tracks and was
not related to logged trees. Thus sylviculture module resulted in
aggregated localized gaps but not in species selective disturbance. We
found that, contrarily to previous results, functional richness was
significantly (\(p<0.01\)) decreasing forest resilience see Figure
\ref{fig:gIeqSylv}). But the range of variation from resilience was
really low (\(2 < I_{eq_{600}} < 10\)). And resilience was mainly due to
the density of \emph{Bocoa prouacensis} in the simulated mature forests.
Effectively \emph{Bocoa prouacensis} was often the main harvested
species and possessed additionnally a quick recovery inside the model
due to unrealisticaly advantageous parameters. Still we found that
functional dispersion was decreasing resilience but not significantly
(see \protect\hyperlink{appendix-6-sylviculture-simulations}{Appendix 6:
Sylviculture simulations}). Finally, biodiversity net effect is almost
undisturbed due to the low disturbance intensity from the sylviculture
module and results did not show complementarity or selection effect in
forest resilience (see
\protect\hyperlink{appendix-6-sylviculture-simulations}{Appendix 6:
Sylviculture simulations}).

\begin{figure}[htbp]
\centering
\includegraphics{master-thesis_files/figure-latex/gIeqSylv-1.pdf}
\caption{\label{fig:gIeqSylv}Ecosystem resilience after 600 years with
taxonomic and functional diversity. Cummulative integral from ecosystem
distance to forest structure equilibrium after 600 years normalized by
disturbed basal area was represented against functional richness
\citep[FRic,][]{villeger_new_2008}. Dot color represents the species
richness (nb) whereas dot size represents the disturbed basal area
(m2/ha). Grey line represents the linear regression and grey area the
confidence interval.}
\end{figure}

@@

Finally, sylviculture module implemented inside TROLL showed lacks of
ability to reproduce selective logging with current design of
experiments. Results did not seem to be usable and will not be
discussed. The main issues was the ability of the model to simulate
mature forest with correct abundancy of mature trees from commonly
harvested species. Two solutions might be possible in the tunning of the
model. First, forest inventories could be used to initialize the model
instead of a bare soil resulting in realistic species abundances,
especially for harvested species. Secondly, selective logging could
focus on guilds of species meeting peculiar values of functional traits
\citep[as wood density, see][]{Huth2004, Khler2004, Ruger2008} allowing
the model to harvest more volume in order to meet reality.

@@

This appendix presents ecosystem resilience after 600 years with
taxonomic and functional diversity for different levels of disturbance.
It encompass all functionnal diversity components \citep[FRIC, FEve,
FDiv, and FDis,][]{villeger_new_2008}. And it presents results for both
forest structure (Figure \ref{fig:A5IeqStructureAll}) and forest
functionning (Figure \ref{fig:A5IeqProductionAll}).

\begin{figure}[htbp]
\centering
\includegraphics{master-thesis_files/figure-latex/A5IeqStructureAll-1.pdf}
\caption{\label{fig:A5IeqStructureAll}Ecosystem resilience after 600 years
with taxonomic and functional diversity for different levels of
disturbance. Cummulative integral from ecosystem distance to forest
structure equilibrium after 600 years was represented against functional
diversity \citep[FRIC, FEve, FDiv, and FDis,][]{villeger_new_2008} for
different level of disturbance (25, 50 and 75\% of total basal area);
dot shapes represents the species richness.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{master-thesis_files/figure-latex/A5IeqProductionAll-1.pdf}
\caption{\label{fig:A5IeqProductionAll}Ecosystem resilience after 600 years
with taxonomic and functional diversity for different levels of
disturbance. Cummulative integral from ecosystem distance to forest
functionning equilibrium after 600 years was represented against
functional diversity \citep[FRIC, FEve, FDiv, and
FDis,][]{villeger_new_2008} for different level of disturbance (25, 50
and 75\% of total basal area); dot shapes represents the species
richness.}
\end{figure}

@@

\hypertarget{appendix-6-sylviculture-simulations}{\section{Appendix 6:
Sylviculture simulations}\label{appendix-6-sylviculture-simulations}}

\subsection{Ecosystem functions}\label{ecosystem-functions-3}

This appendix presents ecosystem resilience after 600 years with
taxonomic and functional diversity after selective logging. It encompass
all functionnal diversity components \citep[FRIC, FEve, FDiv, and
FDis,][]{villeger_new_2008}. And it presents results for both forest
structure (Figure \ref{fig:A6IeqStructureAll}) and forest functionning
(Figure \ref{fig:A6IeqProductionAll}).

\begin{figure}[htbp]
\centering
\includegraphics{master-thesis_files/figure-latex/A6IeqStructureAll-1.pdf}
\caption{\label{fig:A6IeqStructureAll}Ecosystem resilience after 600 years
with taxonomic and functional diversity. Cummulative integral from
ecosystem distance to forest structure equilibrium after 600 years
normalized by disturbed basal area was represented against functional
functional diversity \citep[FRIC, FEve, FDiv, and
FDis,][]{villeger_new_2008}. Dot color represents the species richness
(nb) whereas dot size represents the disturbed basal area (m2/ha). Grey
line represents the linear regression and grey area the confidence
interval.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{master-thesis_files/figure-latex/A6IeqProductionAll-1.pdf}
\caption{\label{fig:A6IeqProductionAll}Ecosystem resilience after 600 years
with taxonomic and functional diversity. Cummulative integral from
ecosystem distance to forest functionning equilibrium after 600 years
normalized by disturbed basal area was represented against functional
functional diversity \citep[FRIC, FEve, FDiv, and
FDis,][]{villeger_new_2008}. Dot color represents the species richness
(nb) whereas dot size represents the disturbed basal area (m2/ha). Grey
line represents the linear regression and grey area the confidence
interval.}
\end{figure}

\subsection{Biodiversity effect}\label{biodiversity-effect-3}

Figure \ref{fig:A6allBE} presents the resilience of complementarity and
selection effects for different ecosystem metrics (AGB, BA, N, GPP and
NPP).

\begin{figure}[htbp]
\centering
\includegraphics{master-thesis_files/figure-latex/A6allBE-1.pdf}
\caption{\label{fig:A6allBE}Resilience of complementarity and selection
effects. Complementarity effect (CE) and selection effect (SE) where
normalized by control net effect (NEc), thus measuring their resilience
over time for different ecosystem variables (AGB, BA, N, GPP).}
\end{figure}
